Draft Research pt2

### 2019-03-10 draftResearch_pt2.Rmd
Clean up of z_score vs z_score_adj comparison

z_batters %>% 
  mutate(type = "Batter") %>%
  bind_rows(z_pitchers) %>%
  select(playerid, Name, type, ADP, z_sum) %>%
  mutate(type = if_else(is.na(type), "Pitcher", type)) %>%
  arrange(z_sum %>% desc()) %>%
  ggplot(aes(x=ADP,y=z_sum,color=type)) +
  geom_point(aes(text=Name)) -> p

@@

fielding %>%
  select(playerid, Pos, E, Def) %>%
  full_join(batters_raw, "playerid") %>%
  filter(ADP < 999) %>%
  select(Name, Team, Pos, E, Def, Fld) %>%
  filter(is.na(E))
  ggplot(aes(x=E,y=Fld)) +
  geom_point()

@@

hist_pitching %>%
  ggplot(aes(x=CG/3,y=IP/3)) +
  geom_point()
```
Looks like there were only two pitchers in the past three years that averaged 1 CG/year with less than 150 IP/year. Takeaway is to weigh IP a bit more.

@@

z_compare_adj %>%
  ggplot(aes(x=ADP,y=z_sum,color=type)) +
  geom_point(aes(text=Name)) -> p_adj

>>>>

z_compare <- z_batters %>% 
  mutate(type = "Batter") %>%
  bind_rows(z_pitchers) %>%
  select(playerid, Name, type, ADP, z_sum) %>%
  mutate(type = if_else(is.na(type), "Pitcher", type)) %>%
  arrange(z_sum %>% desc())

z_compare %>%
  mutate(ovrl_rank = row_number()) %>%
  ggplot(aes(x=ADP,y=ovrl_rank,color=type)) +
  geom_point(aes(text=Name)) +
  geom_abline(slope=1) -> p

@@

fielding %>%
  select(playerid, Pos, E, Def) %>%
  full_join(batters_raw, "playerid") %>%
  filter(ADP < 999) %>%
  select(Name, Team, Pos, E, Def, Fld) %>%
  filter(!is.na(E)) %>%
  ggplot(aes(x=E,y=Fld)) +
  geom_point()

@@

hist_pitching %>%
  ggplot(aes(x=CG/3,y=IP/3)) +
  geom_point()
```
Looks like there were only three pitchers in the past three years that averaged 1 CG/year with less than 150 IP/year. Takeaway is to weigh IP a bit more.

@@

z_compare_adj %>%
  ggplot(aes(x=ADP,y=ovrl_rank,color=type)) +
  geom_point(aes(text=Name)) +
  geom_abline(slope=1)-> p_adj
